---
title: "Covid91 vaccine study Final2020"
author: "Amee Rodrick"
date: "October 26,2020"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(forcats)
OldData <-read.csv(file="covid91.csv",header=TRUE)
#recode aids to say covid and then remove the annoying "X" from the dataframe
FinalData <- OldData %>% mutate(infected = recode(infected, aids = "covid", none = "OK" )) %>% select(-one_of("X"))
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative vaccine (covid91) is under test in clinical trials. Given the nature of this vaccine it is suspected that the drug may exhibit different effectiveness across the variety of subpopulations tracked. Consider population subgroups by gender( guys and gals), drug use, and sexual orientation. Write a complete report that separately considers this drug for each subgroup and your recommendations as to whether people in the subgroup should take the vaccine.

##  Females

```{r}
dataF<-filter(FinalData,sex=="gal")
```

## Results for Females

```{r}
barchartGC(~infected + treatment,data=dataF)
barchartGC(~infected + treatment,data=dataF, type="percent")

```

For the graph, the drug is more effective for the females. Fewer people have gotten sick when taking the drug than when taking the placebo. Approximately 64% of the people took the placebo got sick, wheres as the 36% of the people who took the drug got sick. 

## Numerical Results for Females

```{r}
table1 <- xtabs(~infected + treatment, data=dataF)
rowPerc(table1)
colPerc(table1)
```
## Inferential Results for Females

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->



# Results for Males

```{r}
dataM<-filter(FinalData,sex=="guy")
```


## Graphical Results for Males

```{r}
barchartGC(~infected + treatment,data=dataM)
barchartGC(~infected + treatment,data=dataM, type="percent")
```

For this graph, the drug is not effective for the guys, It appears to not be helping keep the guys from contracting Covid. More people who took the drug got sick then those who took the placebo   

## Numerical Results for Males

```{r}
table1 <- xtabs(~infected + treatment, data=dataM)
rowPerc(table1)
colPerc(table1)

## Inferential Results for Males

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

# Results for LGBTQ

```{r}
dataQ<-filter(FinalData,LGBTQ=="gay")
```

## Graphical Results for LGBTQ

```{r}
barchartGC(~infected + treatment,data=dataQ)
barchartGC(~infected + treatment,data=dataQ, type="percent")
```

For the graph, the drug is more effective for the LGBTQ. Fewer people have gotten sick when taking the drug than when taking the placebo. Approximately 64% of the people took the drug got sick, wheres as the 36% of the people who took the placebo got sick. 



## Numerical Results for LGBTQ

```{r}
table1 <- xtabs(~infected + treatment, data=dataQ)
rowPerc(table1)
colPerc(table1)
```

## Inferential Results for LGBTQ

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

## Results for Drug Users

```{r}
dataD<-filter(FinalData,DrugUser=="yes")
```

## Graphical Results for Drug Users

```{r}
barchartGC(~infected + treatment,data=dataD)
barchartGC(~infected + treatment,data=dataD, type="percent")
```

For the graph, the drug is more effective for the drug users. Fewer people have gotten sick when taking the drug than when taking the placebo. Approximately 64% of the people took the placebo got sick, wheres as the 22% of the people who took the drug got sick. 


## Numerical Results for Drug Users

```{r}
table1 <- xtabs(~infected + treatment, data=dataD)
rowPerc(table1)
colPerc(table1)
```

## Inferential Results for Drug Users

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```




<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->



# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->





